Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)

### 2023-11-13 manuscript_BiSC.tex

>>>>

% --- Performance --- %
The performance of the models varied substantially by pollutant. In table x. performance metrics for the LUR and HM are shown. Hybrid BC model had the best performance of the models assessed, with a higher R\textsuperscript{2} and lower RMSE in all models. The performance of the PM25

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Model} & \textbf{Pollutant} & \textbf{Dataset campaign} & \textbf{N} & \textbf{R\textsuperscript{2} (10-CV)} & \textbf{RMSE (10-CV)} \\ \hline
HM & NO\textsubscript{2} & BiSC-home & 1232 & 0.64 & 7.5 \\ \hline
HM & PM\textsubscript{2.5} & BiSCAPE & 161 & 0.66 & 3.45 \\ \hline
HM & BC & BiSCAPE & 74 & 0.86 & ... \\ \hline
HM & Fe & BiSCAPE & ... & ... & ... \\ \hline
HM & Cu & BiSCAPE & ... & ... & ... \\ \hline
HM & Zn & BiSCAPE & ... & ... & ... \\ \hline
LUR & NO\textsubscript{2} & BiSC-home & ... & ... & ... \\ \hline
LUR & PM\textsubscript{2.5} & BiSCAPE & ... & ... & ... \\ \hline
LUR & BC & BiSCAPE & ... & ... & ... \\ \hline
LUR & Fe & BiSCAPE & ... & ... & ... \\ \hline
LUR & Cu & BiSCAPE & ... & ... & ... \\ \hline
LUR & Zn & BiSCAPE & ... & ... & ... \\ \hline
\end{tabular}
\caption{Your caption here}
\label{table:your_label_here}
\end{table}

% --- Exposure concentrations --- %
Outdoor air pollution concentration exposure during the entire pregnancy for each pollutant and model are shown in FIGURE X. The exposure range was larger for the LUR model

% --- Correlation between measures and model estimates --- %
Spearman correlation of air pollution exposure during the entire pregnancy between measurements, LUR, DM and HM at the residential addresses ranged from r = x to x (figure X).
